\listoffigures
\label{ListOfFigures}
\begin{itemize}
\item GFDL: Gnu Free Documentation License. \url{http://www.gnu.org/licenses/fdl.html}
\item cc-by-sa-3.0:  Creative Commons Attribution ShareAlike 3.0 License. \url{http://creativecommons.org/licenses/by-sa/3.0/} 
\item cc-by-sa-2.5:  Creative Commons Attribution ShareAlike 2.5 License. \url{http://creativecommons.org/licenses/by-sa/2.5/} 
\item cc-by-sa-2.0:  Creative Commons Attribution ShareAlike 2.0 License. \url{http://creativecommons.org/licenses/by-sa/2.0/} 
\item cc-by-sa-1.0:  Creative Commons Attribution ShareAlike 1.0 License. \url{http://creativecommons.org/licenses/by-sa/1.0/} 
\item cc-by-2.0:  Creative Commons Attribution 2.0 License.  \url{http://creativecommons.org/licenses/by/2.0/}  
\item cc-by-2.0:  Creative Commons Attribution 2.0 License. \url{http://creativecommons.org/licenses/by/2.0/deed.en}  
\item cc-by-2.5:  Creative Commons Attribution 2.5 License. \url{http://creativecommons.org/licenses/by/2.5/deed.en}  
\item cc-by-3.0:  Creative Commons Attribution 3.0 License. \url{http://creativecommons.org/licenses/by/3.0/deed.en}  
\item GPL:  GNU General Public License. \url{http://www.gnu.org/licenses/gpl-2.0.txt} 
\item LGPL:  GNU Lesser General Public License. \url{http://www.gnu.org/licenses/lgpl.html}
 \item PD: This image is in the public domain.
\item ATTR:  The copyright holder of this file allows anyone to use it for any purpose, provided that the copyright holder is properly attributed. Redistribution, derivative work, commercial use, and all other use is permitted. 
\item EURO: This is the common (reverse) face of a euro coin. The copyright on the design of the common face of the euro coins belongs to the European Commission. Authorised is reproduction in a format without relief (drawings, paintings, films) provided they are not detrimental to the image of the euro.
\item LFK: Lizenz Freie Kunst. \url{http://artlibre.org/licence/lal/de} 
\item CFR: Copyright free use. 
\item EPL: Eclipse Public License. \url{http://www.eclipse.org/org/documents/epl-v10.php} 
\end{itemize}
Copies of the GPL, the LGPL as well as a GFDL are included in chapter \mylref{Licenses}{Licenses}. Please note that images in the public domain do not require attribution. You may click on the image numbers in the following table to open the webpage of the images in your webbrower.
\pagebreak
\small
\begin{longtable}{|p{0.05\textwidth}|p{0.6\textwidth}|p{0.15\textwidth}|}
\hline
